Stellar Radiation is Critical for Regulating Star Formation and Driving Outflows in Low Mass Dwarf Galaxies

### 2019-04-10 thesis/chapters/ch_introduction.tex
Proof read of introduction updates. New dissertation command

%
% \beq
% \frac{\mathrm{d}}{\mathrm{d}t} \int_S \mathbf{B} \cdot \mathrm{d}S = 0,f
% \eeq
Galaxies are amalgamations of gas and stars embedded in dark matter halos. They are formed over cosmic time as the products of the hierarchical assembly that follows from the collapse of the primordial density fluctuations that arose after the Big Bang. The gravitational pull of dark matter -- as predicted from $\Lambda$CDM cosmology -- controls the hierarchical growth of structure in the Universe. While, broadly speaking, the evolution of baryons is dominated by this pull, the beautiful simplicity of $\Lambda$CDM cosmology is muddied by their existence. The complexities of hydrodynamics, magnetohydrodynamics, thermodynamics, chemistry, radiative processes, and nucleosynthesis -- or, ``astrophysics" for short -- drives these deviations and gives rise to the Universe that we observe. In spite of a concerted effort spanning nearly a century, we are far from a self-consistent theory of galaxy evolution (see \citet{SomervilleDave2015} and \cite{NaabOstriker2017} for recent reviews). It is understanding the rich set of physics that formed our own Galaxy and the countless galaxies scattered throughout the Universe that motivates this work.

A substantial slice of modern astrophysics has been devoted towards understanding the chemical evolution -- the abundances of individual elements in space and time -- of the Universe. With the exception of H, He, and trace amounts of light elements, all of the elements in the Universe are produced in nuclear reactions associated with stellar evolution, either in the cores of stars, stellar winds, asymptotic giant branch (AGB) winds of low mass stars, and more exotic sites like neutron star - neutron star mergers (NS-NS). See \cite{Nomoto2013}, \cite{Thielmann2017}, and \cite{Frebel2018} for recent reviews on this topic as it applies to studies of galactic and stellar evolution. Much work has been done in studying the global metallicity evolution of galaxies through the mass-metallicity relationship \citep[e.g.][]{Lequeux1979,Tremonti2004,Lee2006,Zahid2012,AndrewsMartini2013}, the metallicity gradient in our own and nearby galaxies \citep[e.g.][]{Searle1971,Shaver1983,Belfiore2017,SanchezMenguiano2017}, and detailed stellar abundances in nearby dwarf galaxies with spectroscopically resolved stars \citep[see the review in][]{Tolstoy2009}. Yet in spite of increased number and quality of observations of galactic chemical evolution, developing a complete model of galactic chemical evolution is still a daunting task.

%Developing a complete model for galactic chemical evolution is a daunting task.
To give an impression of the difficulties involved, we outline a recipe for constructing a complete model of galactic chemical evolution. One must first prescribe a galaxy's connection to its large scale structure to understand the inflow of pristine, metal-free gas into the disk of the galaxy, and the accretion (via mergers) of stars formed previously in galaxies hosted by different dark matter halos. One can then worry about knowing where, when, how, and with what masses stars form in the first place from this gas. This requires understanding the hydrodynamic
%and magnetohydrodynamic
properties of the multi-scale, multi-phase turbulent interstellar medium (ISM) and the radiative processes and chemistry that operate within the ISM. This in turn requires one to toss in a detailed understanding of the stellar feedback physics -- stellar radiation, stellar winds, and supernovae -- that helps to regulate star formation by destroying cold, star forming gas, driving the multi-phase structure of the ISM, and by driving outflows of gas into the circumgalactic medium (CGM) around galaxies. Simultaneously, one makes the simple step of nailing down a complete model of stellar structure, stellar evolution, the reaction rates and cross sections of every nuclear reaction, and the lifetimes of individual isotopes. Once all of this is understood, one can then color in the gas in the galaxy over time with the individual metal yields of stellar populations released over their lifetime. With a complete understanding of stellar feedback and the ISM, one can then be sure that they completely capture the mixing of these metals in the ISM over time, and will produce a stellar population with accurate metal abundance ratios. In addition, one would then produce realistic galactic winds, removing the correct amount of metals from the galaxy and enriching the CGM and the intergalactic medium (IGM). Finally, one can layer this model ad nauseum on top of a $\Lambda$CDM model for the cosmological evolution of many galaxies, reproducing all observed properties of galactic chemical evolution as a function of both mass and redshift..... Wait... I forgot about magnetic fields, active galactic nuclei, and cosmic rays...

@@

The following is a primer on how to model galactic evolution in hydrodynamics simulations. We focus on the physics needed to simulate galaxies (cooling, heating, chemistry, star formation, feedback, etc.) as it pertains to the aspects of galactic chemical evolution examined in this \dissertation. This is meant to be a broad overview of the physical processes treated in such simulations, focusing more on aspects of their implementation rather than the derivation of theory behind each process. While important, the latter is beyond the scope of this introduction and would readily turn into a full textbook. Focusing on implementation gives a much more accurate representation of the actual work done and skills learned during work on this \dissertation. This discussion includes a very brief overview of hydrodynamics and the numerical methods used in this work in Section~\ref{intro:sec:hydrodynamics}, nucleosynthesis and stellar evolution in Section~\ref{intro:sec:nucleosynthesis}, radiative cooling and chemistry (actual chemistry) in Section~\ref{intro:sec:cooling}, star formation and star particles in Section~\ref{intro:sec:sf} and Section~\ref{intro:sec:stars}, and stellar feedback in Section~\ref{intro:sec:feedback}.

But first, we note that Astronomy jargon is full of idiosyncrasies. As mentioned before, the word ``chemical" in ``galactic chemical evolution" is a bit of a misnomer. This is commonly applied simply to refer to studies interested in the evolution of metal abundances (either as a whole, or for individual isotopes) in galaxies over time, and less often to the chemical reactions that those elements may participate in. Unfortunately ``chemistry" is often used with both meanings in the same work requiring context to decipher the intended meaning. Likewise, ``metals" refers broadly to every element except H and He. Throughout this \dissertation we often refer to the metallicity ($Z$) of a galaxy, its gas, or its stars. This quantity represents the total mass fraction of all metals -- and is computed as such in our simulations -- but we note that it is generally impossible to measure the abundances of all metals in astrophysical contexts outside our own Solar System (and even then, it is challenging). The metallicity of our own Sun ($Z_{\odot}$), for example, is still uncertain \citep{Asplund2009}. Instead, most observational works adopt Fe as a proxy for total metallicity in stars (due to its many, strong absorption lines), O as a proxy in gas-phase abundances in the ISM (as it is the most abundant metal in the Universe and has convenient, strong emission lines), and O or C in gas-phase abundances of the CGM when observed in absorption (primarily through the lines OVI and CIV). These metallicity proxies are usually reported in some form of normalized abundance ratio. For stellar metallicities, this is given in the form [A/B]. [A/B] = log($N_A / N_B$) - log($N_A / N_B$)$_{\odot}$, where $N$ refers to the number of atoms of a given element (e.g. [Fe/H]). Confusingly, gas-phase abundances are commonly reported as just log($N_A / N_B$), often with the somewhat arbitrary normalization of +12, or log(O/H) + 12, for example; converting between the two definitions is straightforward (albeit annoying) and requires adopting a value for the solar abundance. \footnote{This is not to mention issues in normalization across methods of deriving these abundances... \citep[e.g.][]{KewleyEllison2008}.}

@@

In this \dissertation, we make use of the adaptive-mesh refinement (AMR) hydrodynamics code \code{Enzo}, as described in greater detail in Chapter~\ref{ch:chapter1}. As it pertains to galactic chemical evolution, however, the use of a grid-based code has the advantage that metals (which are advected as passive scalars that follow the fluid-flow in the simulations) are allowed to mix and diffuse naturally across fluid elements (grid cells). This is not possible in native SPH implementations, yet is necessary to reproduce realistic galactic chemical evolution properties as shown by multiple recent works testing implementations of diffusion in SPH simulations \citep[e.g.][]{Shen2010,Su2017a,Escala2018}. The disadvantage of the diffusion in \code{Enzo}, however, is that it is entirely numerical, and therefore its exact properties are challenging to characterize and are strongly resolution dependent. Throughout this \dissertation we attempt to account for the effects of resolution on our results, but do not explicitly examine the properties of numerical diffusion itself.

@@

This means that elements from different nucleosynthetic channels are produced on different timescales during a galaxy's evolution, as set by the lifetimes of the stars in which they occur, and are released into the galaxy at different energies, with different spatial distributions within the galaxy, and at different rates. For example, O, an $\alpha$-element is produced predominately in massive stars and is therefore released via core collapse supernovae on timescales of $\sim$~10~Myr after a star formation event, near their stellar birth sites. By contrast, Sr is produced predominately via the s-process (discussed more below) which occurs in part in the asymptotic giant branch (AGB) winds of lower mass stars ($M < 8$~M$_{\odot}$) at much lower energies and on timescales of $\sim 100$~Myr - $1$~Gyr. By this time, these stars would have diffused farther away from their birth sites, potentially sampling a qualitatively different portion of the ISM than the preceeding core collapse SNe. Generally, how different timescales affect observed stellar abundances patterns are well understood and easily modeled.\footnote{The canonical example of this is the ``knee" feature in a $[\alpha/$Fe] vs. [Fe/H] diagram, where the location of this knee signifies the point at which Type Ia enrichment (which produces significant Fe, but little to no $\alpha$ elements) begins to have a significant contribution over core collapse SNe (rich in $\alpha$ elements, but not Fe) \citep[e.g.[]{MatteucciBrocato1990, Geisler2005, Hill2018}. The location of this knee in this diagram shifts for a given galaxy depending on its SFH.} However, it is not well understood how differences in where and with what energies these events occur affect observed stellar abundance patterns. Investigating these differences is a key motivation of this \dissertation.

As relevant to this work, we briefly summarize a few of the important nucleosynthetic channels shown in Figure~\ref{intro:fig:periodic table} and their sites. $\alpha$-elements, notably O, Mg, Si, Ca, and Ti, are produced during the lifetime of massive stars (O, Mg) or during the core collapse supernova explosion itself. In either case, these elements are synthesized through the capture of an $\alpha$ nucleus, progressing towards increasingly heavier nuclei in intervals of 4/2 in mass/atomic number (as $\alpha$ = $^{4}_2$He) from $^8_4$Be all the way to the stable $^{52}_{26}$Fe and unstable $^{56}_{28}$Ni (which days to $^{56}_{26}$Fe). The iron group elements, notably Fe, Mn, Co, and Ni, are produced predominately in Type Ia supernovae, with variations depending on a single vs. double degenerate scenario, the initial composition of exploding white dwarf(s) (WD), and the dynamics of the explosion itself.

@@

Finally, although the production of elements unaffected by the r-process are comparatively well understood, there are still large uncertainties in both nuclear reaction rates and stellar evolution properties that affect the computed yields for any given element. As including self-consistent nuclear reactions in the interior of stars is nearly computationally impossible in galaxy-scale simulations, metal yields are generally included as averaged over an entire stellar population (see Section\ref{intro:sec:stars}) as obtained from a tabulated set of yields. These yields for a given star in a simulation are typically IMF-averaged, and occasionally mass and metallicity dependent depending on the level of detail desired in the simulation. Often, only the global metallicity is tracked in simulations, but tracking individual metal species (especially C, O, and Si which can affect the chemistry and cooling physics in the ISM) is becoming more common. The uncertainties across tabulated yields, however, mean there are often significant variations and inconsistencies between tables produced by separate groups. These can sometimes make interpreting the results of galactic chemical evolution models challenging.

@@

A full, detailed model of radiative cooling, heating, non-equillibrium chemistry, and dust is generally far too computationally expensive to include in galaxy-scale simulations. For this reason, many large-scale cosmological simulations assume that all gas is optically thin and that all molecules and ionization states exist in equilibrium. This allows for the quick use of tabulated look-up tables for radiative cooling and heating, often produced using \code{cloudy} \citep{Cloudy2013}, that depend on gas density, temperature, metallicity, and redshift (which sets the UVB heating rate). More complex simulations often track some number (usually $< 10$) of species involved in primordial chemistry in order to better account for non-equilibrium effects and \Hmolecular production, though with noted increases in memory requirements and computational cost. Some of the most advance models to-date can account for well over 10$^2$ individual chemical reactions involving $>$ 20 elements and molecules \citep[e.g.][]{Richings2016,Richings2018}; but these are typically prohibitively expensive to run on large scales. In this \dissertation we adopt the chemistry and radiative cooling and heating physics models available in the newly developed, open-source library \code{GRACKLE} \citep{GrackleMethod}. The exact physics included in our simulations are discussed in greater detail in Chapter~\ref{ch:chapter1}, but we note that improvements to \code{GRACKLE} have been made as the direct result of the research conducted during this \dissertation.
%mention that I made improvements to this?

@@

In galaxy-scale hydrodynamics, the costs in resolving the spatial scales and gas densities required to directly follow star formation relegates this process to a sub-grid model. Stars form from fluid elements that surpass a variety of threshold conditions at an assumed rate and efficiency. Usually, simulators set these thresholds to fully encompass gas whose Jeans-length (and thus dynamical behavior) becomes unresolved according to the widely-used \cite{Truelove1997} criterion. Often, gas is required to surpass a simple mass or number density threshold, on top of which simulators can also require that the local gas cells be in a converging flow ($\nabla \cdot \bm{v} < 0$), that gas surpass some virial threshold (describing how bound a cloud may be)
%cite?,
or that gas meet a minimum \Hmolecular mass fraction \citep[e.g.][]{Kuhlen2012}
%\citep[e.g.][]{}
. Once a fluid element is flagged as star forming, simulators have a few options to choose from in how to determine what fraction and with what rate that mass is converted into stars. Briefly, some form of the following equation is usually adopted to describe the star formation rate density,
\begin{equation}
\label{intro:eq:sfr}
 \dot{\rho}_{\rm SF} = \epsilon \frac{\rho_{\rm gas}}{t_*},
\end{equation}
where $\rho_{\rm gas}$ is the local gas density, $\epsilon$ is some fixed or variable star formation efficiency, and the timescale, $t_*$, is often adopted as the local free fall time, or
\begin{equation}
  t_* = t_{\rm ff} = \sqrt{\frac{3\pi}{32 \rm{G} \rho_{\rm gas}}}.
\end{equation}
In many cases, $\epsilon$ is fixed to some small value ($\sim$ 0.01) \citep{KrumholzTan2007} meant to represent a galaxy-scale average of star formation efficiency, even though this may vary significantly between individual molecular clouds \citep{Grudic2018}. High-resolution simulations, where the mass of stars that would form in a single time step ($dt \times \rm{SFR}$) is far less than a single star particle mass, allow stars to form out of star forming fluid elements stochastically \citep[e.g.][]{Goldbaum2015}.

@@

In this \dissertation, we develop the first implementation that breaks the SSP formalism entirely by following stars as individual star particles sampled from an adopted IMF. This allows us to place unprecedented detail on both the stellar feedback and metal yields associated with each star, spatially and temporally resolving differences in both of these channels as a function of stellar mass and metallicity.

@@

Although not included in this \dissertation, for the sake of completeness, we mention a few additional sources of stellar feedback that likely contribute to the full picture of galactic evolution. A substantial amount of recent research has been dedicated towards the examination of supernova-driven cosmic ray feedback (see Section~\ref{ch1:sec:CRs} for a more detailed discussion and references). In brief, cosmic rays can be a dominant source of heating in very dense gas and act as a source of non-thermal pressure in the ISM, which can drive galactic winds with qualitatively different phase structures \citep[e.g.][]{SalemBryanCorlies}. Binarity is often ignored in models of stellar feedback. The effects of binary evolution can dramatically extend the timescales over which ionizing radiation and supernovae act in a newly formed stellar populations. Typically, this increases their total energy output and decreases the ISM densities in which SNe explode, increasing their effectiveness (see Section~\ref{ch1:sec:binary stars}). Finally, exotic sources of stellar feedback, such as hypernovae, high-mass X-ray binaries, and NS-NS mergers can also be a potentially important sources of feedback, particularly in the lowest mass halos \citep[e.g.][]{Artale2015}. However, the uncertainties in the frequency and delay time distributions for when these events should occur, and their relative rarity, preclude including these effects in this \dissertation.

@@

High resolution simulations, like those developed in this \dissertation, can typically rely on using pure thermal energy injection while still avoiding artificial overcooling.\footnote{This is advantageous because it is often substantially easier to implement than kinetic / momentum injection methods while being less susceptible to numerical artifacts, especially for grid-based codes.} This is true for simulations with typical spatial / mass resolutions better than a few pc / 10 M$_{\odot}$ \citep{Simpson2015,Hu2018,Smith2018b}. However, a spatial resolution requirement is a density dependent statement; in this case supernovae that occur in the densest gas ($n > 10^{2-3}$~cm$^{-3}$) may still be under-resolved and ineffective. In this case, accounting for feedback processes from massive stars that occur before the first core collapse SN in a given star formation event becomes critical \citep{Hu2016}. Including these physics, as discussed below, greatly reduces the typical ISM densities in which SNe occur, greatly increasing the likelihood that these events are well resolved.

@@

Non-ionizing radiation also contributes to the regulation of star formation and the multi-phase ISM. Far ultraviolet (FUV) photons contribute to gas heating via the photoelectric heating of dust grains. This is a significant heating mechanism in higher metallicity environments, like the Milky Way \citep{Parravano2003,Wolfire2003}, but may still be important in setting temperature floor of cold dense gas in lower mass galaxies \citep{Forbes2016,Hu2017}. Lyman-Werner (LW) band radiation regulates the \Hmolecular~ abundance, which is particularly important in low-metallicity environments where \Hmolecular~ is a dominant coolant \citep[e.g.][]{Glover2003,Wolcott-Green2012}.\footnote{And is arguably even more important when using star formation perscriptions that depend upon the local \Hmolecular mass fraction.} As the goal of this \dissertation is to develop an as-complete-as-possible model of galactic chemical evolution, we account for each of these processes in some fashion.

>>>>

%
% \beq
% \frac{\mathrm{d}}{\mathrm{d}t} \int_S \mathbf{B} \cdot \mathrm{d}S = 0,f
% \eeq
Galaxies are amalgamations of gas and stars embedded in dark matter halos. They are formed over cosmic time as the products of the hierarchical assembly that follows from the collapse of the primordial density fluctuations which arose after the Big Bang. The gravitational pull of dark matter -- as predicted from $\Lambda$CDM cosmology -- controls the hierarchical growth of structure in the Universe. While, broadly speaking, the evolution of baryons is dominated by this pull, the beautiful simplicity of $\Lambda$CDM cosmology is muddied by their existence. The complexities of hydrodynamics, magnetohydrodynamics, thermodynamics, chemistry, radiative processes, and nucleosynthesis -- or, ``astrophysics" for short -- drives these deviations and gives rise to the Universe that we observe. In spite of a concerted effort spanning nearly a century, we are far from a self-consistent theory of galaxy evolution (see \citet{SomervilleDave2015} and \cite{NaabOstriker2017} for recent reviews). It is understanding the rich set of physics that formed our own Galaxy and the countless galaxies scattered throughout the Universe that motivates this work.

A substantial slice of modern astrophysics has been devoted towards understanding the chemical evolution -- the abundances of individual elements in space and time -- of the Universe. With the exception of H, He, and trace amounts of light elements, all of the elements in the Universe are produced in nuclear reactions associated with stellar evolution, either in the cores of stars, stellar winds, asymptotic giant branch (AGB) winds of low mass stars, and more exotic sites like neutron star - neutron star mergers (NS-NS). See \cite{Nomoto2013}, \cite{Thielmann2017}, and \cite{Frebel2018} for recent reviews on this topic as it applies to studies of galactic and stellar evolution. Much work has been done in studying the global metallicity evolution of galaxies through the mass-metallicity relationship \citep[e.g.][]{Lequeux1979,Tremonti2004,Lee2006,Zahid2012,AndrewsMartini2013}, the metallicity gradient in our own and nearby galaxies \citep[e.g.][]{Searle1971,Shaver1983,Belfiore2017,SanchezMenguiano2017}, and detailed stellar abundances in nearby dwarf galaxies with spectroscopically resolved stars \citep[see the review in][]{Tolstoy2009}. Yet in spite of increased number and quality of observations tracing galactic chemical evolution, developing a complete model of galactic chemical evolution is still a daunting task.

%Developing a complete model for galactic chemical evolution is a daunting task.
To give an impression of the difficulties involved, we outline a recipe for constructing a complete model of galactic chemical evolution. One must first prescribe a galaxy's connection to its large scale structure to understand the inflow of pristine, metal-free gas and growth of its gaseous disk, and the accretion (via mergers) of stars formed previously in galaxies hosted by different dark matter halos. One can then worry about knowing where, when, how, and with what masses stars form in the first place from this gas. This requires understanding the hydrodynamic
%and magnetohydrodynamic
properties of the multi-scale, multi-phase turbulent interstellar medium (ISM) and the radiative processes and chemistry that operate within the ISM. This in turn requires one to toss in a detailed understanding of the stellar feedback physics -- stellar radiation, stellar winds, and supernovae -- that helps to regulate star formation by destroying cold, star forming gas, driving the multi-phase structure of the ISM, and by driving outflows of gas into the circumgalactic medium (CGM) around galaxies. Simultaneously, one must make the simple step of nailing down a complete model of stellar structure, stellar evolution, the reaction rates and cross sections of every nuclear reaction, and the lifetimes of individual isotopes. Once all of this is understood, one can then color in the gas in the galaxy over time with the individual metal yields of stellar populations released over their lifetime. With a complete understanding of stellar feedback and the ISM, one can then be sure that they completely capture the mixing of these metals in the ISM over time, and will produce a stellar population with accurate metal abundance ratios. In addition, one would then produce realistic galactic winds, removing the correct amount of metals from the galaxy and enriching the CGM and the intergalactic medium (IGM). Finally, one can layer this model ad nauseum on top of a $\Lambda$CDM model for the cosmological evolution of many galaxies, reproducing all observed properties of galactic chemical evolution as a function of both mass and redshift..... Wait... I forgot about magnetic fields, active galactic nuclei, and cosmic rays...

@@

The following is a primer on how to model galactic evolution in hydrodynamics simulations. We focus on the physics needed to simulate galaxies (cooling, heating, chemistry, star formation, feedback, etc.) as it pertains to the aspects of galactic chemical evolution examined in this \Dissertation. This is meant to be a broad overview of the physical processes treated in such simulations, focusing more on aspects of their implementation rather than the derivation of theory behind each process. While important, the latter is beyond the scope of this introduction and would readily turn into a full textbook. Focusing on implementation gives a much more accurate representation of the actual work done and skills learned during this \Dissertation. This discussion includes a very brief overview of hydrodynamics and the numerical methods used in this work in Section~\ref{intro:sec:hydrodynamics}, nucleosynthesis and stellar evolution in Section~\ref{intro:sec:nucleosynthesis}, radiative cooling and chemistry (actual chemistry) in Section~\ref{intro:sec:cooling}, star formation and star particles in Section~\ref{intro:sec:sf} and Section~\ref{intro:sec:stars}, and stellar feedback in Section~\ref{intro:sec:feedback}.

But first, we note that Astronomy jargon is full of idiosyncrasies. As mentioned before, the word ``chemical" in ``galactic chemical evolution" is a bit of a misnomer. This is commonly applied simply to refer to studies interested in the evolution of metal abundances (either as a whole, or for individual isotopes) in galaxies over time, and less often to the chemical reactions that those elements may participate in. Unfortunately ``chemistry" is often used with both meanings in the same work requiring context to decipher the intended meaning. ``Metals" refers broadly to every element except H and He. Throughout this \dissertation we often refer to the metallicity ($Z$) of a galaxy, its gas, or its stars. This quantity represents the total mass fraction of all metals -- and is computed as such in our simulations -- but we note that it is generally impossible to measure the abundances of all metals in astrophysical contexts outside our own Solar System (and even then, it is challenging). The metallicity of our own Sun ($Z_{\odot}$), for example, is still uncertain \citep{Asplund2009}. Instead, most observational works adopt Fe as a proxy for total metallicity in stars (due to its many, strong absorption lines), O as a proxy in gas-phase abundances in the ISM (as it is the most abundant metal in the Universe and has convenient, strong emission lines), and O or C in gas-phase abundances of the CGM when observed in absorption (primarily through the lines OVI and CIV). These metallicity proxies are usually reported in some form of normalized abundance ratio. For stellar metallicities, this is given in the form [A/B] = log($N_A / N_B$) - log($N_A / N_B$)$_{\odot}$, where $N$ refers to the number of atoms of a given element (e.g. [Fe/H]). Confusingly, gas-phase abundances are commonly reported as just log($N_A / N_B$), often with the somewhat arbitrary normalization of +12, or log(O/H) + 12, for example; converting between the two definitions is straightforward (albeit annoying) and requires adopting a value for the solar abundance. \footnote{This is not to mention issues in normalization across methods of deriving these abundances... \citep[e.g.][]{KewleyEllison2008}.}

@@

In this \Dissertation, we make use of the adaptive-mesh refinement (AMR) hydrodynamics code \code{Enzo}, as described in greater detail in Chapter~\ref{ch:chapter1}. As it pertains to galactic chemical evolution, however, the use of a grid-based code has the advantage that metals (which are advected as passive scalars that follow the fluid-flow in the simulations) are allowed to mix and diffuse naturally across fluid elements (grid cells). This is not possible in native SPH implementations, yet is necessary to reproduce realistic galactic chemical evolution properties as shown by multiple recent works testing implementations of diffusion in SPH simulations \citep[e.g.][]{Shen2010,Revaz2016,Hirai2017,Su2017a,Escala2018}. The disadvantage of the diffusion in \code{Enzo}, however, is that it is entirely numerical. Therefore, its exact properties are challenging to characterize and are resolution dependent. Throughout this \dissertation we attempt to account for the effects of resolution on our results, but do not explicitly examine the properties of numerical diffusion itself.

@@

This means that elements from different nucleosynthetic channels are produced on different timescales during a galaxy's evolution, as set by the lifetimes of the stars in which they occur, and are released into the galaxy at different energies, with different spatial distributions within the galaxy, and at different rates. For example, O, an $\alpha$-element is produced predominately in massive stars and is therefore released via core collapse supernovae on timescales of $\sim$~10~Myr after a star formation event, near their stellar birth sites. By contrast, Sr is produced predominately via the s-process (discussed more below) which occurs in part in the asymptotic giant branch (AGB) winds of lower mass stars ($M < 8$~M$_{\odot}$) at much lower energies and on timescales of $\sim 100$~Myr - $1$~Gyr. By this time, these stars would have diffused farther away from their birth sites, potentially sampling a qualitatively different portion of the ISM than the preceeding core collapse SNe. Generally, how different timescales affect observed stellar abundances patterns are well understood and easily modeled.\footnote{The canonical example of this is the ``knee" feature in a $[\alpha/$Fe] vs. [Fe/H] diagram, where the location of this knee signifies the point at which Type Ia enrichment (which produces significant Fe, but little to no $\alpha$ elements) begins to have a significant contribution over core collapse SNe (rich in $\alpha$ elements, but not Fe) \citep[e.g.[]{MatteucciBrocato1990, Geisler2005, Hill2018}. The location of this knee in this diagram shifts for a given galaxy depending on its SFH.} However, it is not well understood how differences in where and with what energies these events occur affect observed stellar abundance patterns. Investigating these differences is a key motivation of this \Dissertation.

As relevant to this work, we briefly summarize a few of the important nucleosynthetic channels shown in Figure~\ref{intro:fig:periodic table} and their sites. $\alpha$-elements, notably O, Mg, Si, Ca, and Ti, are produced during the lifetime of massive stars (O, Mg) or during the core collapse supernova explosion itself. In either case, these elements are synthesized through the capture of an $\alpha$ nucleus, progressing towards increasingly heavier nuclei in intervals of 4/2 in mass/atomic number (as $\alpha$ = $^{4}_2$He) from $^8_4$Be all the way to the stable $^{52}_{26}$Fe and unstable $^{56}_{28}$Ni (which decays to $^{56}_{26}$Fe). The iron group elements, notably Fe, Mn, Co, and Ni, are produced predominately in Type Ia supernovae, with variations depending on a single vs. double degenerate scenario, the initial composition of exploding white dwarf(s) (WD), and the dynamics of the explosion itself.

@@

Finally, although the production of elements unaffected by the r-process are comparatively well understood, there are still large uncertainties in both nuclear reaction rates and stellar evolution properties that affect the computed yields for any given element. As including self-consistent nuclear reactions in the interior of stars is nearly computationally impossible in galaxy-scale simulations, metal yields are generally included as averaged over an entire stellar population (see Section\ref{intro:sec:stars}) as obtained from a tabulated set of yields. The yields for a given star in a simulation are typically IMF-averaged, and occasionally mass and metallicity dependent depending on the level of detail desired in the simulation. Often, only the global metallicity is tracked in simulations, but tracking individual metal species (especially C, O, and Si which can affect the chemistry and cooling physics in the ISM) is becoming more common. The uncertainties across tabulated yields, however, mean there are often significant variations and inconsistencies between tables produced by separate groups. These can sometimes make interpreting the results of galactic chemical evolution models challenging.

@@

A full, detailed model of radiative cooling, heating, non-equillibrium chemistry, and dust is generally far too computationally expensive to include in galaxy-scale simulations. For this reason, many large-scale cosmological simulations assume that all gas is optically thin and that all molecules and ionization states exist in equilibrium. This allows for the quick use of tabulated look-up tables for radiative cooling and heating, often produced using \code{cloudy} \citep{Cloudy2013}, that depend on gas density, temperature, metallicity, and redshift (which sets the UVB heating rate). More complex simulations often track some number (usually $< 10$) of species involved in primordial chemistry in order to better account for non-equilibrium effects and \Hmolecular~production, though with noted increases in memory requirements and computational cost. Some of the most advance models to-date can account for well over 10$^2$ individual chemical reactions involving $>$ 20 elements and molecules \citep[e.g.][]{Richings2016,Richings2018}; but these are typically prohibitively expensive to run on large scales. In this \dissertation we adopt the chemistry and radiative cooling and heating physics models available in the newly developed, open-source library \code{GRACKLE} \citep{GrackleMethod}. The exact physics included in our simulations are discussed in greater detail in Chapter~\ref{ch:chapter1}, but we note that improvements to \code{GRACKLE} have been made as the direct result of the research conducted during this \Dissertation.
%mention that I made improvements to this?

@@

In galaxy-scale hydrodynamics, the costs in resolving the spatial scales and gas densities required to directly follow star formation relegates this process to a sub-grid model. Stars form from fluid elements that surpass a variety of threshold conditions at an assumed rate and efficiency. Usually, simulators set these thresholds to fully encompass gas whose Jeans-length (and thus dynamical behavior) becomes unresolved according to the widely-used \cite{Truelove1997} criterion. Often, gas is required to surpass a simple mass or number density threshold, on top of which simulators can also require that the local gas cells be in a converging flow ($\nabla \cdot \bm{v} < 0$), that gas surpass some virial threshold (describing how bound a cloud may be)
%cite?,
or that gas meet a minimum \Hmolecular~mass fraction \citep[e.g.][]{Kuhlen2012}
%\citep[e.g.][]{}
. Once a fluid element is flagged as star forming, simulators have a few options to choose from in how to determine what fraction and with what rate that mass is converted into stars. Briefly, some form of the following equation is usually adopted to describe the star formation rate density,
\begin{equation}
\label{intro:eq:sfr}
 \dot{\rho}_{\rm SF} = \epsilon \frac{\rho_{\rm gas}}{t_*},
\end{equation}
where $\rho_{\rm gas}$ is the local gas density, $\epsilon$ is some fixed or variable star formation efficiency, and the timescale, $t_*$, is often adopted as the local free fall time, or
\begin{equation}
  t_* = t_{\rm ff} = \sqrt{\frac{3\pi}{32 \rm{G} \rho_{\rm gas}}}.
\end{equation}
In many cases, $\epsilon$ is fixed to some small value ($\sim$ 0.01) \citep{KrumholzTan2007} meant to represent a galaxy-scale average of star formation efficiency, even though this may vary significantly between individual molecular clouds \citep{Grudic2018}. High-resolution simulations, where the mass of stars that would form in a single time step ($dt \times \rm{SFR}$) is far less than a single star particle mass, allow stars to form out of star forming fluid elements stochastically \citep[e.g.][]{Goldbaum2015}.

@@

In this \Dissertation, we develop the first implementation that breaks the SSP formalism entirely by following stars as individual star particles sampled from an adopted IMF. This allows us to place unprecedented detail on both the stellar feedback and metal yields associated with each star, spatially and temporally resolving differences in both of these channels as a function of stellar mass and metallicity.

@@

Although not included in this \Dissertation, for the sake of completeness, we mention a few additional sources of stellar feedback that likely contribute to the full picture of galactic evolution. A substantial amount of recent research has been dedicated towards the examination of supernova-driven cosmic ray feedback (see Section~\ref{ch1:sec:CRs} for a more detailed discussion and references). In brief, cosmic rays can be a dominant source of heating in very dense, optically-thick gas and act as a source of non-thermal pressure in the ISM, which can drive galactic winds with qualitatively different phase structures \citep[e.g.][]{SalemBryanCorlies}. Binarity is often ignored in models of stellar feedback. The effects of binary evolution can dramatically extend the timescales over which ionizing radiation and supernovae act in a newly formed stellar populations. Typically, this increases their total energy output and decreases the ISM densities in which SNe explode, increasing their effectiveness (see Section~\ref{ch1:sec:binary stars}). Finally, exotic sources of stellar feedback, such as hypernovae, high-mass X-ray binaries, and NS-NS mergers can also be a potentially important sources of feedback, particularly in the lowest mass halos \citep[e.g.][]{Artale2015}. However, the uncertainties in the frequency and delay time distributions for when these events should occur, and their relative rarity, preclude including these effects in this \Dissertation.

@@

High resolution simulations, like those developed in this \Dissertation, can typically rely on using pure thermal energy injection while still avoiding artificial overcooling.\footnote{This is advantageous because it is often substantially easier to implement than kinetic / momentum injection methods while being less susceptible to numerical artifacts, especially for grid-based codes.} This is true for simulations with typical spatial / mass resolutions better than a few pc / 10 M$_{\odot}$ \citep{Simpson2015,Hu2018,Smith2018b}. However, a spatial resolution requirement is a density dependent statement; in this case supernovae that occur in the densest gas ($n > 10^{2-3}$~cm$^{-3}$) may still be under-resolved and ineffective. In this case, accounting for feedback processes from massive stars that occur before the first core collapse SN in a given star formation event becomes critical \citep{Hu2016}. Including these physics, as discussed below, greatly reduces the typical ISM densities in which SNe occur, greatly increasing the likelihood that these events are well resolved.

@@

Non-ionizing radiation also contributes to the regulation of star formation and the multi-phase ISM. Far ultraviolet (FUV) photons contribute to gas heating via the photoelectric heating of dust grains. This is a significant heating mechanism in higher metallicity environments, like the Milky Way \citep{Parravano2003,Wolfire2003}, but may still be important in setting temperature floor of cold dense gas in lower mass galaxies \citep{Forbes2016,Hu2017}. Lyman-Werner (LW) band radiation regulates the \Hmolecular~abundance, which is particularly important in low-metallicity environments where \Hmolecular~is a dominant coolant \citep[e.g.][]{Glover2003,Wolcott-Green2012}.\footnote{And is arguably even more important when using star formation prescriptions that depend upon the local \Hmolecular~mass fraction.} As the goal of this \dissertation is to develop an as-complete-as-possible model of galactic chemical evolution, we account for each of these processes in some fashion.

The simplest way to model stellar radiation feedback is to apply an optically thin, analytic radiation profile, such as the galaxy-centered exponential photoelectric heating profile used in \cite{Tasker2009}, or $1/r^2$ profiles from individual sources \citep[e.g.][]{Forbes2016}. However, radiative transfer effects, such as gas self-shielding, are often important, particularly for ionizing radiation. Solving the equations of radiative transfer directly in simulations -- as is done with ray tracing methods -- is computationally expensive and scales significantly with the number of sources. For this reason, approximate methods, such as flux-limited diffusion, treat radiation as a fluid, removing the scaling of computational cost with the number of sources. In this \Dissertation, we follow the evolution of galaxies that have at most $10 - 100$ ionizing sources at one time, making it computationally feasible to use the accurate adaptive ray-tracing radiative transfer method implemented in \code{Enzo}.
